Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-06-02 LaTeX_paper/paper.tex
add reference template

\section{Abstract}
The jigsaw puzzle problem has been in the eye of computer scientists for a while,
and some clever solutions have already been found. These algorithms are made to
work with a “digital” jigsaw puzzle \ref{fig:figure_digital_puzzle},
but there aren't papers (at least not popular enough to be searchable)
that try to apply the solution
to a “real world” jigsaw puzzle \ref{fig:figure_real_puzzle}.\newline
The problem has been tackled by some small projects. But, as said earlier,
the process and eventual challenges has never been documented by a full paper,
this wants to be the first.\newline
As a bonus the paper will also cover the creation of a user friendly app
that will be open source and free to use.

@@

    \subsubsection{The Solver:} This component  uses the information provided by the
    Comparator \ref{document:comparator}, and tries to find a solution
    (i.e.\ a position and an orientation for each piece)
    that is the most likely to be correct.\label{document:solver}

@@

\end{document}

>>>>

\section{Abstract}
The jigsaw puzzle problem has been in the eye of computer scientists for a while,
and some clever solutions have already been found. These algorithms are made to
work with a “digital” jigsaw puzzle~\ref{fig:figure_digital_puzzle},
but there aren't papers (at least not popular enough to be searchable)
that try to apply the solution
to a “real world” jigsaw puzzle~\ref{fig:figure_real_puzzle}.\newline
The problem has been tackled by some small projects. But, as said earlier,
the process and eventual challenges has never been documented by a full paper,
this wants to be the first.\newline
As a bonus the paper will also cover the creation of a user friendly app
that will be open source and free to use.

@@

    \subsubsection{The Solver:} This component  uses the information provided by the
    Comparator~\ref{document:comparator}, and tries to find a solution
    (i.e.\ a position and an orientation for each piece)
    that is the most likely to be correct.\label{document:solver}

@@

\cite{lamport94}

\begin{thebibliography}{9}

  \bibitem{lamport94}
    Leslie Lamport,
    \textit{\LaTeX: a document preparation system},
    Addison Wesley, Massachusetts,
    2nd edition,
    1994.

  \end{thebibliography}\end{document}
